D3064R0: Bringing the Laws of Physics to Bear on the OOTA Problem

### 2024-01-11 ootavacuous.tex
Add per-code semantic dependencies as union over executions
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

>>>>

But what if you really need a definition of semantic dependency
for a given code fragment that covers all executions?
One approach is to take the union of semantic dependencies across
all executions, which might be useful when carrying out static analysis.
On the other hand, many C++ implementations carry out specialization
optimizations, which consider groups of executions.
For example, an implementation might special-case a \co{NULL} pointer when
considering several inline functions that take early exits in that case.
Tools working with such implementations might therefore choose to focus
on executions corresponding to a given specialization when generating
semantic dependencies for code corresponding to that specialization.
